Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-02 rainbowCAM.tex
Wrote some text for the Results (2) section.

\title{Scattering from compact objects: Regge poles \\ and the Complex Angular Momentum method}

@@

The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}. A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}. A dimensionless parameter,
\begin{equation}
M \omega = \pi \frac{r_g}{\lambda},
\end{equation}
encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (henceforth we adopt geometric units such that $G=c=1$). The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods. The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been covered.

@@

Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$. % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ property of $h(r)$. The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V_{\ell}^{\text{ax}} &= - \frac{3Mf(R)}{R^3} ,
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} .
\end{equation}

@@

 \subsection{Numerical results}\label{subsec:results}
In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$ close to the Buchdahl bound. Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.

@@

The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the axial \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles'' for a scalar wave on a stellar background. The radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell} \rightarrow V_{\ell}^{\text{ax}}$ where \cite{Cardoso:2014sna}
\begin{eqnarray}\label{RW_Potentiel_axialGW}
V_{\ell}^{\text{ax}}(r) = f(r)\bigg[\frac{\ell(\ell+1)}{r^2}  - \dfrac{3 h(r)}{2r}\left(\dfrac{f'(r)}{f(r)}+\dfrac{h'(r)}{h(r)}\right) & \nonumber \\
	 + 8 \pi (p - \rho) & \bigg] .
\end{eqnarray}
%
We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.

Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency. Both types of pole satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition of a purely outgoing wave in the far field
%
\begin{equation}\label{bc_pole_inf}
\phiout (r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
\displaystyle{  A^{(+)}_{\lambda-1/2} (\omega) e^{+i\omega r_\ast}}.
\end{equation}
%
Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phireg$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
\begin{equation}\label{Wronskian}
  W[\phireg, \phiout ]= 0
\end{equation}
It has been shown that, the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in certain regions, buy using the standard WKB approximation. In the high-frequency domain we have (see Refs \ldots)
\begin{equation}\label{Approx_origin}
  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*) \quad\quad 0\leq r_*\leq R_*
\end{equation}
where $j_{\lambda-1/2}$ is the spherical Bessel function of the first kind and
\begin{equation}
\label{Approx_infinity}
\phiout  \scriptstyle{\underset{\omega \to \infty}{=}}
\left\{
\begin{aligned}
&e^{i\omega(r_*-R_*)}+\mathcal{R} e^{-i\omega (r_*-R_*)}& \scriptstyle{1/\omega\leq r_{*} < R_*,}\\
&\left(1+\mathcal{R}\right) e^{i\omega(r_*-R_*)}        & \scriptstyle{R_*\leq r_{*}<\infty.}
\end{aligned}
\right.
\end{equation}
Here
\begin{equation}\label{R_star}
  R_*=\int_{0}^{R}\, dr\,\frac{1}{\sqrt{f(r)h(r)}}
\end{equation}
and $\mathcal{R}$ is a reflection coefficient with the defintion given in Ref.~\cite{Berry_1982}.
Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
\begin{equation}\label{R_reflection_1}
  \mathcal{R} = a \omega^{-2}
\end{equation}
with
\begin{eqnarray}
% \nonumber % Remove numbering (before each equation)
  a &=& -\left(\frac{i}{2}\right)^2 \lim_{\epsilon\to 0^{+}} \left[V_{\lambda-1/2}(r)\Bigg{|}_{r=R+\epsilon}-V_{\lambda-1/2}(r)\Bigg{|}_{r=R-\epsilon}\right] \nonumber\\
   &=& \frac{3M(R-2M)}{4 R^4}
\end{eqnarray}

%\begin{equation}\label{a_def}
%a= \frac{3M \left(R-2M\right)^2}{4 R^5}.
%\end{equation}
Now, by inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} \cite{nist},
\begin{equation}\label{Approx_origin_bis}
  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
\end{equation}
and Eq. \eqref{Approx_infinity} into the condition  \eqref{Wronskian}, we obtain
\begin{equation}\label{WKB_1}
   e^{ i\pi (\lambda-1/2)- 2 i \omega R_*}=-\mathcal{R}.
\end{equation}
%
We then solve Eq.~\eqref{WKB_1} and we obtain
\begin{equation}\label{lambda_Approx}
  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{1}{\mathcal{R}}\right)
\end{equation}
This corresponds to the series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost constant  imaginary part. Of course, they lie in the first quadrant of the CAM plan with a positive real part
%
\begin{equation}\label{Real_Part}
  \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)>0.
\end{equation}
%
The overtones are labelled by $n =1,2,\ldots$ and $n$ has an upper limit
%
\begin{equation}\label{Limit_Broad_RP}
n \leq \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor.
\end{equation}
%
In other words, there is a finite number of the ``broad Regge poles''.

@@

\begingroup
\squeezetable
\begin{table}[htp]
\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}. The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
\smallskip
\centering
\begin{ruledtabular}
\begin{tabular}{cccc}
 $n$ & $\omega$  & $\lambda^{\text{(B-R)}}_n(\omega)$ & $\lambda^{\text{(B-R, WKB)}}_n(\omega)$
 \\ \hline
$1$  & $3$  & $1.56219+2.33072 i$  & $1.592793+2.189767i$   \\
     & $16$ & $ 0.62529+3.27098 i$ & $0.661564+3.255453i $   \\

@@

\section{Scattering and CAM theory}

@@

We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
\begin{equation}\label{Scalar_Scattering_diff}
  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
\end{equation}
where
\begin{equation}\label{Scalar_Scattering_amp}
 \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
\end{equation}
denotes the scattering amplitude.  In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.  We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation

@@

To construct the CAM representation, we follow the steps in section~II of the Ref~\cite{Folacci:2019cmc} and recall the main results.

By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
\begin{equation}\label{SWT_gen}
\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
\end{equation}
with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$). By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
\end{eqnarray}
In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).

@@

It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{PR_def_Am}
A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
\end{equation}
The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{residues_RP}
r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
\end{equation}
These residues play a central role in the complex angular momentum paradigm.

Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions. This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec. IIB~3 and Fig.~1). We obtain

>>>>

\title{Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method}

@@

The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}. A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}. A dimensionless parameter,
\begin{equation}
M \omega = \frac{\pi r_g}{\lambda},
\end{equation}
encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (henceforth we adopt geometric units such that $G=c=1$). The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods. The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been covered.

@@

Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$. % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ property of $h(r)$. The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V_{\ell}^{\text{ax}} &= - \frac{3Mf(R)}{R^3} ,
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} . \label{def:DeltaV}
\end{equation}

@@

 \subsection{Numerical results: the spectrum}\label{subsec:results1}
In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$ close to the Buchdahl bound. Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.

@@

Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models. Here, we adapt the method to obtain analytical approximations for the ``broad resonances'' for waves on a stellar background. The starting point is with the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).

Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency. Both types of pole satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition of a purely outgoing wave in the far field
%
\begin{equation}\label{bc_pole_inf}
\phiout (r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
\displaystyle{  A^{(+)}_{\lambda-1/2} (\omega) e^{+i\omega r_\ast}}.
\end{equation}
%
Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phireg$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$), viz.,
\begin{equation}\label{Wronskian}
  W[\phireg, \phiout ]= 0 .
\end{equation}
It has been shown \cite{Zhang:2011pq} that the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using the standard WKB approximation. In the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Refs \ldots \sam{Please fill this in})
\begin{equation}\label{Approx_origin}
  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*),  \quad\quad 0\leq r_*\leq R_* ,
\end{equation}
where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind and
\begin{equation}
\label{Approx_infinity}
\phiout  \scriptstyle{\underset{\omega \to \infty}{=}}
\left\{
\begin{aligned}
&e^{i\omega(r_*-R_*)}+\mathcal{R} e^{-i\omega (r_*-R_*)}& \scriptstyle{1/\omega\leq r_{*} < R_*,}\\
&\left(1+\mathcal{R}\right) e^{i\omega(r_*-R_*)}        & \scriptstyle{R_*\leq r_{*}<\infty.}
\end{aligned}
\right.
\end{equation}
Here $R_*$ is the tortoise coordinate at the surface of the body, 
\begin{equation}\label{R_star}
  R_*=\int_{0}^{R}\, dr\,\frac{1}{\sqrt{f(r)h(r)}}
\end{equation}
and $\mathcal{R}$ is a reflection coefficient with the definition given in Ref.~\cite{Berry_1982}.
Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, a compact body with a constant density)
\begin{equation}\label{R_reflection_1}
  \mathcal{R} = \alpha \omega^{-2}
\end{equation}
with
\begin{eqnarray}
% \nonumber % Remove numbering (before each equation)
  \alpha &=& \frac{1}{4} \Delta V(R) = \pm \frac{3M(R-2M)}{4 R^4} ,
\end{eqnarray}
where $\Delta V$ is the discontinuity in the effective potential at the surface, defined in Eq.~(\ref{def:DeltaV}), and the $+$ ($-$) sign is chosen for scalar field (axial gravitational wave) cases.

%\begin{equation}\label{a_def}
%a= \frac{3M \left(R-2M\right)^2}{4 R^5}.
%\end{equation}
Now, by inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} \cite{nist},
\begin{equation}\label{Approx_origin_bis}
  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
\end{equation}
and Eq. \eqref{Approx_infinity} into the condition  \eqref{Wronskian}, we obtain
\begin{equation}\label{WKB_1}
   e^{ i\pi (\lambda-1/2)- 2 i \omega R_*}=-\mathcal{R}.
\end{equation}
%
We then solve Eq.~\eqref{WKB_1} to obtain
\begin{equation}\label{lambda_Approx}
  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
\end{equation}
\sam{Please double-check this formula is correct for both scalar (+) and axial GW (-) cases.}
This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}. 
The formula also correctly accounts for the alternating sequence of the scalar-field and axial-GW modes.
 %Of course, they lie in the first quadrant of the CAM plan with a positive real part

The overtones are labelled by $n =1,2,\ldots$ and the condition $\text{Re} \, \lambda_n > 0$ leads to an upper limit for $n$ of %
\begin{equation}\label{Limit_Broad_RP}
n \leq \left\lfloor \frac{\omega R_*}{\pi} \mp \frac{1}{4}\right\rfloor.
\end{equation}
%
In other words, there are a finite number of the broad resonances in the first quadrant.

Table \ref{tab:table5} compares the numerically-determined Regge poles with the WKB approximation in Eq.~(\ref{lambda_Approx}),  for the scalar-field case. The data shows that, while the leading-order WKB approximation captures the essential features of the broad resonance branch, it is not particularly accurate. Higher-order extensions are possible, but not pursued here.

@@

\begingroup
\squeezetable
\begin{table}[htp]
\caption{\label{tab:table5} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}. The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
\smallskip
\centering
\begin{ruledtabular}
\begin{tabular}{cccc}
 $n$ & $2 M \omega$  & $\lambda^{\text{(B-R)}}_n(\omega)$ & $\lambda^{\text{(B-R, WKB)}}_n(\omega)$
 \\ \hline
$1$  & $3$  & $1.56219+2.33072 i$  & $1.592793+2.189767i$   \\
     & $16$ & $ 0.62529+3.27098 i$ & $0.661564+3.255453i $   \\

@@

\section{Scattering and CAM theory}
In this section we calculate the scattering cross section $d\sigma / d\Omega$ by means of the Complex Angular Momentum (CAM) method, and we compare with results obtained in the standard way from a partial-wave series \cite{Dolan:2017rtj}.

@@

For a scalar field, the differential scattering cross section is given by
\begin{equation}\label{Scalar_Scattering_diff}
  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
\end{equation}
where
\begin{equation}\label{Scalar_Scattering_amp}
 \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
\end{equation}
is the scattering amplitude (for details see e.g.~\cite{Dolan:2017rtj} and references therein).  In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}, and the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) were defined in Eq.~(\ref{Matrix_S}).

@@

To construct the CAM representation of $\hat{f}(\theta)$, we follow the steps in section~II of Ref.~\cite{Folacci:2019cmc} and recall the main results below.

The Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} permits us to replace a sum with an integral, viz.,
\begin{equation}\label{SWT_gen}
\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)} ,
\end{equation}
where $F(\cdot)$ is any function without singularities on the real $\lambda$ axis. Applying this to Eq.~(\ref{Scalar_Scattering_amp}) allows us to replace the discrete sum over the ordinary angular momentum $\ell$ with a contour integral in the complex $\lambda$ plane (that is, in the complex $\ell$ plane with $\lambda = \ell +1/2$). By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
\end{eqnarray}
In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.~1 in Ref~\cite{Folacci:2019cmc}).

@@

It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
\begin{equation}\label{PR_def_Am}
A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0,
\end{equation}
with $n=1,2,3,\ldots$
The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{residues_RP}
r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
\end{equation}
These residues play a central role in the complex angular momentum paradigm.

Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions. This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec. IIB~3 and Fig.~1). We obtain
%
\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
\end{equation}
where
\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
\end{equation}
is a background integral contribution with
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
\end{equation}
and
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right. \right.\nonumber \\
&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right).
\end{eqnarray}
\end{subequations}
The second term in Eq.~(\ref{CAM_Scalar_Scattering_amp_tot}) ,
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta),
\end{eqnarray}
is a sum over the Regge poles lying in the first quadrant of the CAM plane. Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}). From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with a corresponding approximation of the differential scattering cross section via (\ref{Scalar_Scattering_diff}).
